UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-04-11 paper/paper.tex
add skeleton of design to the paper

\documentclass[]{final_report}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{csvsimple}
\usepackage{float}
\usepackage[]{algorithm2e}

@@

\emph{/* High level design of the algorithm in pseudo-code? */}

\subsection{Calculate cost per hour for a given pricing scheme}

\begin{algorithm}[H]
 \KwData{Upfront cost, Per hour charge, Utilisation [hours per day];}
 \KwResult{Total cost per hour for a given pricing scheme defined as \textit{cph};}
 read upfront\;
 read perhour\;
 read hours\;	
 return (upfront + (365 * perhour * hours)) / (365 * hours)
 \caption{Calculate cost per hour for a given pricing scheme}
\end{algorithm}

\subsection{Calculate intersection points to find out the best pricing scheme for a number of hours/day utilization}

@@

\subsection{Collect VM usage data}

@@

\subsection{Group usage metrics by machine}

\begin{algorithm}[H]
 \KwData{VM usage data;}
 \KwResult{Metrics containing calculated duration and day;}
 read vmMetrics\;
 \ForAll{line in vmMetrics} {
        calculateDuration();
        calculateDay();
 }
\caption{VM metrics transformation}

\subsection{Calculate number of hours/day, distance from optimality points, CPU and memory utilization}

\subsection{Suggest changes to the least optimal VMs considering SLAs based on CPU and memory utilization}

@@

>>>>

\documentclass[]{final_report}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{csvsimple}
\usepackage{float}
\usepackage[]{algorithm2e}
\usepackage{titlesec}
\setcounter{secnumdepth}{4}
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

@@

\subsection{Data gathering, transformation and analytics}

\subsubsection{Calculate cost per hour for a given pricing scheme}

\begin{algorithm}[H]
 \KwData{Upfront cost, Per hour charge, Utilization [hours per day];}
 \KwResult{Total cost per hour for a given pricing scheme defined as \textit{cph};}
 read upfront\;
 read perhour\;
 read hours\;	
 return (upfront + (365 * perhour * hours)) / (365 * hours)
 \caption{Calculate cost per hour for a given pricing scheme}
\end{algorithm}

\subsubsection{Calculate intersection points to find out the best pricing scheme for a number of hours/day utilization}

@@

\subsubsection{Metrics collection}

@@

        8,CPU capacity,FLOAT,YES

        9,Memory capacity,FLOAT,YES

\subsubsection{Daily metrics aggregation}

\paragraph{Calculate uptime per machine}
Input: Job start and end time logged for each machine in a form of \textless K, List\textless V\textgreater\textgreater

Output: Uptime based on span between min start time and max end time \textless K,V\textgreater

\paragraph{Aggregate CPU and memory usage}
Input: Sampled CPU and memory usage logged per job in a form of \textless K, List\textless V\textgreater\textgreater

Output: Aggregated resource usage \textless K,V\textgreater

\paragraph{Calculate number of jobs per day}
Input: Job id per machine \textless K, List\textless V\textgreater\textgreater

Output: Job count per machine \textless K,V\textgreater

\paragraph{Calculate cluster averages for aggregations}
Input: Aggregated CPU, memory and number of tasks per machine per day \textless K, List\textless V\textgreater\textgreater

Output: Averages for CPU, memory and number of tasks \textless K, List\textless V\textgreater\textgreater

\paragraph{Calculate distance from optimality points based on uptime}
Input: Machine uptime per day

Output: Distance from optimality points. Might be positive or negative.

\subsection{Recognize inefficiencies and suggest changes}

\subsubsection{Threshold based report}

Generate report of machines based on distance from optimality points. Use customizable threshold. 
Results from the report will be used to calculate suggestions.

\subsubsection{Visual recognition}

Visual recognition as a helper method to define thresholds, especially for further incremental optimizations. 
Useful as static thresholds can miss a whole set of machines that are just below the threshold.

\begin{figure}[H]
        \includegraphics[width=\linewidth]{figures/cubism}
        \caption{Visualization of distance from optimality points. Green - positive, Blue - negative values.}
        \label{fig:cubism}
\end{figure}

\subsubsection{Squeeze-them-in suggestion strategy}

Input: results of the Threshold based report.

Computation: Calculate spare capacity based on average CPU and memory usage. Iterate through a pool of available machines (not included in input report) and advertise available capacity only if CPU and memory usage is lower than average. Aggregate spare capacity results.

Output: List of machines that can be shutdown based on computed spare-capacity.

\subsubsection{New capacity configuration suggestion}

Input: results of the Threshold based report.

Computation: Compute a minimal number of VMs for each configuration based on requested capacity

Output: A number and configuration of the cheapest computed configuration.

@@

\subsection{Recognize inefficiencies and suggest changes}

\subsubsection{Threshold based report}

Generate report of machines based on distance from optimality points. Use customizable threshold. 
Results from the report will be used to calculate suggestions.

\subsubsection{Visual recognition}
